---

title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill

---


```{r setup, include = FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(p8105.datasets)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(
    y = ~price, color = ~neighbourhood, 
    type = "box", colors = "viridis"
  )
```

Column {data-width=350}
-----------------------------------------------------------------------
### Chart B

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(
    x = ~neighbourhood, y = ~n,
    type = "bar")
```


### Chart C

```{r}
ggp_scatterplot = 
  nyc_airbnb %>% 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point()

ggplotly(ggp_scatterplot)
```


However, the website’s _site.yml file conflicts with the dashboard’s YAML header regarding the output format – and the website’s _site.yml “wins”. To address this issue, instead of knitting you can use this command to knit the dashboard.

rmarkdown::render("dashboard_template.Rmd", output_format = "flexdashboard::flex_dashboard")
This will create dashboard_template.html but not open it in RStudio’s Viewer pane; you can open the file in a browser instead. Alternatively, using RStudio’s Build pane to Build Website will produce the same results. To illustrate, we’ll put the dashboard we just created on a website for this topic.

All of this YAML business is only an issue for dashboards embedded in websites; a standalone dashboard (in a non-website GH repo or R Project) can be knit using the same process as other .Rmd files.